Response to reviewers

### 2025-01-27 Manuscript/main_ecography_R2.tex
Update main_ecography_R2.tex

\begin{table}[ht]
\caption{Glossary and equivalence of terms used in this papers; adapted from \cite{guillerme2018disprity} and \cite{mammola2021concepts}.}
\centering
\begin{tabular}{p{2.5cm}p{4cm}p{5cm}p{5cm}}
Term in this paper & definition & in ecology & in macroevolution \\
\hline
Trait space & Matrix ($n \times d$) with a structural relation between rows and columns & Functional space, morphospace , etc. & Morphospace, traitspace, etc.  \\
\hline
Observations & Rows ($n$) & Taxa, field sites, environments, etc. & Taxa, specimen, populations, elements, OTUs etc. \\
\hline
Dimensions & Columns ($d$) & Traits, Ordination scores, distances, etc. & Traits, ordination scores, distances, etc. \\
\hline
Traits & Columns subset ($b \times n$; $b \leq d$) & uni/multidimensional characteristic*; e.g. geographical location & uni/multidimensional characteristic; e.g. landmark coordinates \\
\hline
Group & Rows subset ($m \times d$; $m \leq n$) & Treatments, phylogenetic group (clade), etc. & Clades, geological stratum, etc. \\
\hline
Metric & Statistic (i.e. a measure) & Dissimilarity index or metric, hypervolume, functional diversity, etc. & Disparity metric or index \\
\hline
Stressors & An algorithm removing a proportion of the observations & Introduction of invasive species, change of landscape use, climate change, pollution, experimental design, etc. & Mass extinction, Tectonic change, climate change, etc. \\
\hline
Stressors' intensity & The amount of observation removed (percentages) & Proportion of species affected, proportion of temperature change, etc. & Severity of mass extinction,  etc. \\
\hline
\end{tabular}
* Note that our definition of a trait is a generalisation of \cite{violle2007let,mcgill2006rebuilding,dawson2021traits}'s suggestions which is expanded to include traits beyond the ones used for functional ecology (macroevolution, palaeontology, microbiology, etc.).
\end{table}

@@

\begin{table}
\center
\scriptsize
\begin{tabular}{p{0.2\linewidth}|p{0.2\linewidth}|p{0.4\linewidth}|p{0.2\linewidth}}
\textbf{Approximated mechanism (biological)} & \textbf{Used mechanism (algorithm in \texttt{dispRity::reduce.space})} & \textbf{Stressor description} & \textbf{Type of metric expected to recover the mechanism}\\
\hline
  Null mechanism & Random removal (``random'') & No overall systematic change in observations' traits or community structure except for the reduction in the number of observations. & Metrics sensitive to the amount of data \\

@@

\begin{table}
\center
\scriptsize
\begin{tabular}{p{0.1\linewidth}|p{0.15\linewidth}|p{0.15\linewidth}|p{0.2\linewidth}|p{0.15\linewidth}|p{0.1\linewidth}}

@@

\end{tabular}
\caption{\scriptsize{\textbf{Functional diversity metrics tested in our simulations.}}
}
\label{Tab:metrics}
* The \texttt{TPD} package currently only allows calculations for traitspaces up to four dimensions. This metric was exclude from traitspaces with more than four dimensions.
\end{table}

@@

We tested 12 trait space occupancy metrics on simulated and empirical datasets to assess how each metric captures patterns of trait space changes based on stressors approximating ecological and evolutionary mechanisms.
Our results show that different metrics capture different patterns (what) leading to inferring different processes (how) that can be proposed to explain different mechanisms (why).
Therefore, the choice of trait space occupancy metric is essential to accurately describe a pattern of interest.
We found that different metrics can capture changes in pattern relative to the null mechanisms in different ways depending on the approximated mechanism of interest.
For example, for the approximated equalising mechanism, most metrics capture a pattern clearly smaller than the one from the null mechanism (i.e. randomly removing elements has more effects on the metric than removing them following the mechanism).
However, some metrics (e.g. the Functional evenness based on the hypervolume) capture a pattern clearly greater than the one from the null mechanism.
This means that changes in metric values can be counter intuitive and should always been interpreted in the context of the metric, data and question at hand.
Note also that, as mentioned above, different dimensionalities can have different effects on the metrics, depending on both the traitspace and the metric nature \citep{bellman1957dynamic}.

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.5\textwidth]{Figures/empirical_example.pdf}
\caption{Example of a traitspace based on the empirical data described above.}
\label{Fig:trait_space_example}
\end{figure}
\bigskip

>>>>

\begin{table}[htbp]
\caption{Glossary and equivalence of terms used in this papers; adapted from \cite{guillerme2018disprity} and \cite{mammola2021concepts}.}
\centering
\begin{tabular}{p{2.5cm}p{4cm}p{5cm}p{5cm}}
Term in this paper & definition & in ecology & in macroevolution \\
\hline
Trait space & Matrix ($n \times d$) with a structural relation between rows and columns & Functional space, morphospace , etc. & Morphospace, trait space, etc.  \\
\hline
Observations & Rows ($n$) & Taxa, field sites, environments, etc. & Taxa, specimen, populations, elements, OTUs, etc. \\
\hline
Dimensions & Columns ($d$) & Traits, Ordination scores, distances, etc. & Traits, ordination scores, distances, etc. \\
\hline
Traits & Columns subset ($b \times n$; $b \leq d$) & uni/multidimensional characteristic*; e.g. geographical location & uni/multidimensional characteristic; e.g. landmark coordinates \\
\hline
Group & Rows subset ($m \times d$; $m \leq n$) & Treatments, phylogenetic group (clade), etc. & Clades, geological stratum, etc. \\
\hline
Metric & Statistic (i.e. a measure) & Dissimilarity index or metric, hypervolume, functional diversity, etc. & Disparity metric or index \\
\hline
Stressors & An algorithm removing a proportion of the observations & Introduction of invasive species, change of landscape use, climate change, pollution, experimental design, etc. & Mass extinction, Tectonic change, climate change, etc. \\
\hline
Stressors' intensity & The amount of observation removed (percentages) & Proportion of species affected, proportion of temperature change, etc. & Severity of mass extinction, amount of co-occurring species, etc. \\
\hline
\end{tabular}
* Note that our definition of a trait is a generalisation of \cite{violle2007let,mcgill2006rebuilding,dawson2021traits}'s suggestions which is expanded to include traits beyond the ones used for functional ecology (macroevolution, palaeontology, microbiology, etc.).
\end{table}

@@

\begin{table}[htbp]
\center
\scriptsize
\begin{tabular}{p{0.2\linewidth}|p{0.2\linewidth}|p{0.4\linewidth}|p{0.2\linewidth}}
\textbf{Approximated mechanism (biological)} & \textbf{Used mechanism (algorithm in \texttt{dispRity::reduce.space})} & \textbf{Stressor description} & \textbf{Type of metric expected to recover the mechanism}\\
\hline
  Null mechanism & Random removal (``random'') & No overall systematic change in observations' traits or community structure except for the reduction in the number of observations. & Metrics sensitive to the amount of data \\

@@

\begin{table}[htbp]
\center
\scriptsize
\begin{tabular}{p{0.1\linewidth}|p{0.15\linewidth}|p{0.15\linewidth}|p{0.2\linewidth}|p{0.15\linewidth}|p{0.1\linewidth}}

@@

\end{tabular}
\caption{\scriptsize{\textbf{Functional diversity metrics tested in our simulations.}}
}
\label{Tab:metrics}
* The \texttt{TPD} package currently only allows calculations for trait spaces up to four dimensions. This metric was exclude from trait spaces with more than four dimensions.
\end{table}

@@

We tested 12 trait space occupancy metrics on simulated and empirical datasets to assess how each metric captures patterns of trait space changes based on stressors approximating ecological and evolutionary mechanisms.
Our results show that different metrics capture different patterns (what) leading to inferring different processes (how) that can be proposed to explain different mechanisms (why).
Therefore, the choice of trait space occupancy metric is essential to accurately describe a pattern of interest.
We found that different metrics can capture changes in pattern relative to the null mechanisms in different ways depending on the approximated mechanism of interest.
For example, for the approximated equalising mechanism, most metrics capture a pattern clearly smaller than the one from the null mechanism (i.e. randomly removing elements has more effects on the metric than removing them following the mechanism).
However, some metrics (e.g. the Functional evenness based on the hypervolume) capture a pattern clearly greater than the one from the null mechanism.
This means that changes in metric values can be counter intuitive and should always been interpreted in the context of the metric, data and question at hand.
Note also that, as mentioned above, different dimensionalities can have different effects on the metrics, depending on both the trait space and the metric nature \citep{bellman1957dynamic}.

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.5\textwidth]{Figures/empirical_example.pdf}
\caption{Example of a trait space based on the empirical data described above.}
\label{Fig:trait_space_example}
\end{figure}
\bigskip
